Robust Fault-Tolerant Control and Motion Planning of UAVs and Biped Robots Team System for Search and Rescue Usage

### 2022-11-02 paper/paper.tex
UAV simulation, parameter adjustment. Add actual control input figure

\subsection{motion planning of flying of UAV}
A dynamic model about how the UAV moves in the physical world is given first. By Newton-Euler equation, the dynamic model of UAV can be formulated as \cite{sabatino2015quadrotor}:
\begin{equation} \label{eq:uav} 
    \begin{split}
        \begin{bmatrix}
            f \\ \tau
        \end{bmatrix}&=\begin{bmatrix}
            mI & 0 \\ 0 & J
        \end{bmatrix}\begin{bmatrix}
            \ddot{X} \\ \ddot{\Theta}
        \end{bmatrix}+\begin{bmatrix}
            0 \\ \dot{\Theta}\times(J\dot{\Theta})
        \end{bmatrix}+\begin{bmatrix}
            f_g \\ 0
        \end{bmatrix}
        \\
        &+\begin{bmatrix}
            K_F & 0 \\
            0 & K_\tau
        \end{bmatrix}\begin{bmatrix}
            \dot{X} \\ \dot{\Theta}
        \end{bmatrix}
        % form 2
        % &R(\Theta)=\begin{bmatrix*}[l]
        %     \cos\theta\cos\phi & \sin\phi\sin\theta\cos\psi-\cos\phi\sin\psi & R_1 \\
        %     \cos\theta\sin\phi & R_2 & R_3 \\
        %     -\sin\theta & \sin\phi\cos\theta & R_4
        % \end{bmatrix*}
        % \\
        % &R_1=\cos\phi\sin\theta\cos\psi+\sin\phi\sin\psi
        % \\
        % &R_2=\sin\phi\sin\theta\sin\psi+\cos\phi\cos\psi
        % \\
        % &R_3=\cos\phi\sin\theta\sin\psi-\sin\phi\cos\psi
        % \\
        % &R_4=\cos\phi\cos\theta
    \end{split}
\end{equation}
where $J=\begin{bmatrix}
    J_{x} & 0 & 0 \\
    0 & J_{y} & 0 \\
    0 & 0 & J_{z}
\end{bmatrix}$, $K_F=\begin{bmatrix}
    K_{x} & 0 & 0 \\
    0 & K_{y} & 0 \\
    0 & 0 & K_{z}
\end{bmatrix}$, $K_\tau=\begin{bmatrix}
    K_{\tau_x} & 0 & 0 \\
    0 & K_{\tau_y} & 0 \\
    0 & 0 & K_{\tau_z}
\end{bmatrix}$, $f =\begin{bmatrix}
    f_x \\ f_y \\ f_z
\end{bmatrix} = R(\Theta)\begin{bmatrix}
    0 \\ 0 \\ F
\end{bmatrix}$, $\tau=\begin{bmatrix}
    \tau_x \\ \tau_y \\ \tau_z
\end{bmatrix}$, $X=\begin{bmatrix}
    x \\ y \\ z
\end{bmatrix}$, $\Theta=\begin{bmatrix}
    \phi \\ \theta \\ \psi
\end{bmatrix}$, $f_g=\begin{bmatrix}
    0 \\ 0 \\ -mg
\end{bmatrix}$, $R(\Theta)=R_z(\psi)R_y(\theta)R_x(\phi)$, $R_z(\psi)=\begin{bmatrix} % form 1
    \cos\psi & -\sin\psi & 0 \\
    \sin\psi & \cos\psi & 0 \\
    0 & 0 & 1
\end{bmatrix}$, $R_y(\theta)=\begin{bmatrix}
    \cos\theta & 0 & \sin\theta \\
    0 & 1 & 0 \\
    -\sin\theta & 0 & \cos\theta
\end{bmatrix}$, $R_x(\phi)=\begin{bmatrix}
    1 & 0 & 0 \\
    0 & \cos\phi & -\sin\phi \\
    0 & \sin\phi & \cos\phi
\end{bmatrix}$.
% where $y'$ denotes the $y$ axis after rotating the $z$ axis and $x''$ denotes the $x$ axis after rotating the $y'$ axis
$g$ is the gravity acceleration, $m$ and $J$ is the mass and inertia matrix of UAV, respectively, $\tau$ and $f$ are the total touque and force acting on UAV, respectively, $\Theta$ is the Euler angles in body frame, $X$ is the postion of center of mass (CoM) in inertial frame, $K_\tau$ and $K_F$ are the aerodynamic damping coefficients, $R(\Theta)$ is the intrinsic rotation matrix from body frame to inertial frame, and $F$ is the total thrust. This model treats the UAV as a mass point and can control the force in the $z$ direction and the touque in the $x$, $y$ and $z$ direction. Hence, the reference trajectory of UAV $r(t)=[x_r(t),y_r(t),z_r(t),\phi_r(t),\theta_r(t),\psi_r(t)]^T\in\mathbb{R}^{6}$, where the subscript $r$ denote the reference.

>>>>

\subsection{motion planning of flying of UAV}
A dynamic model about how the UAV moves in the physical world is given first. By Newton-Euler equation, the dynamic model of UAV can be formulated as \cite{sabatino2015quadrotor}:
\begin{equation} \label{eq:uav} 
    \begin{split}
        \begin{bmatrix}
            F \\ \tau
        \end{bmatrix}&=\begin{bmatrix}
            mI & 0 \\ 0 & J
        \end{bmatrix}\begin{bmatrix}
            \ddot{X} \\ \ddot{\Theta}
        \end{bmatrix}+\begin{bmatrix}
            0 \\ \dot{\Theta}\times(J\dot{\Theta})
        \end{bmatrix}+\begin{bmatrix}
            f_g \\ 0
        \end{bmatrix}
        \\
        &+\begin{bmatrix}
            K_F & 0 \\
            0 & K_\tau
        \end{bmatrix}\begin{bmatrix}
            \dot{X} \\ \dot{\Theta}
        \end{bmatrix}
        % form 2
        % &R(\Theta)=\begin{bmatrix*}[l]
        %     \cos\theta\cos\phi & \sin\phi\sin\theta\cos\psi-\cos\phi\sin\psi & R_1 \\
        %     \cos\theta\sin\phi & R_2 & R_3 \\
        %     -\sin\theta & \sin\phi\cos\theta & R_4
        % \end{bmatrix*}
        % \\
        % &R_1=\cos\phi\sin\theta\cos\psi+\sin\phi\sin\psi
        % \\
        % &R_2=\sin\phi\sin\theta\sin\psi+\cos\phi\cos\psi
        % \\
        % &R_3=\cos\phi\sin\theta\sin\psi-\sin\phi\cos\psi
        % \\
        % &R_4=\cos\phi\cos\theta
    \end{split}
\end{equation}
where $J=\begin{bmatrix}
    J_{x} & 0 & 0 \\
    0 & J_{y} & 0 \\
    0 & 0 & J_{z}
\end{bmatrix}$, $K_F=\begin{bmatrix}
    K_{x} & 0 & 0 \\
    0 & K_{y} & 0 \\
    0 & 0 & K_{z}
\end{bmatrix}$, $K_\tau=\begin{bmatrix}
    K_{\tau_x} & 0 & 0 \\
    0 & K_{\tau_y} & 0 \\
    0 & 0 & K_{\tau_z}
\end{bmatrix}$, $F =\begin{bmatrix}
    f_x \\ f_y \\ f_z
\end{bmatrix} = R(\Theta)\begin{bmatrix}
    0 \\ 0 \\ F
\end{bmatrix}$, $\tau=\begin{bmatrix}
    \tau_x \\ \tau_y \\ \tau_z
\end{bmatrix}$, $X=\begin{bmatrix}
    x \\ y \\ z
\end{bmatrix}$, $\Theta=\begin{bmatrix}
    \phi \\ \theta \\ \psi
\end{bmatrix}$, $f_g=\begin{bmatrix}
    0 \\ 0 \\ -mg
\end{bmatrix}$, $R(\Theta)=R_z(\psi)R_y(\theta)R_x(\phi)$, $R_z(\psi)=\begin{bmatrix} % form 1
    \cos\psi & -\sin\psi & 0 \\
    \sin\psi & \cos\psi & 0 \\
    0 & 0 & 1
\end{bmatrix}$, $R_y(\theta)=\begin{bmatrix}
    \cos\theta & 0 & \sin\theta \\
    0 & 1 & 0 \\
    -\sin\theta & 0 & \cos\theta
\end{bmatrix}$, $R_x(\phi)=\begin{bmatrix}
    1 & 0 & 0 \\
    0 & \cos\phi & -\sin\phi \\
    0 & \sin\phi & \cos\phi
\end{bmatrix}$.
% where $y'$ denotes the $y$ axis after rotating the $z$ axis and $x''$ denotes the $x$ axis after rotating the $y'$ axis
$g$ is the gravity acceleration, $m$ and $J$ is the mass and inertia matrix of UAV, respectively, $\tau$ and $F$ are the total touque and force acting on UAV, respectively, $\Theta$ is the Euler angles in body frame, $X$ is the postion of center of mass (CoM) in inertial frame, $K_\tau$ and $K_F$ are the aerodynamic damping coefficients, and $R(\Theta)$ is the intrinsic rotation matrix from body frame to inertial frame. This model treats the UAV as a mass point and can control the force in the $z$ direction and the touque in the $x$, $y$ and $z$ direction. Hence, the reference trajectory of UAV $r(t)=[x_r(t),y_r(t),z_r(t),\phi_r(t),\theta_r(t),\psi_r(t)]^T\in\mathbb{R}^{6}$, where the subscript $r$ denote the reference.
